MS Regressions

### 2022-02-17 msdepression_regressions_started_20211118.Rmd
updated msdepression script

@@

@@

@@

volume_lost_dep_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network)

volume_lost_dep10_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network)

@@

#loss doesn't seem to be different between those with depression and those without
loss_in_dep_network <- lm(total_fascicle_prop_lost_indepnet~depGroupVar, data = depression_network_and_dx_subgroup) #non sig
loss_in_dep_network_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~depGroupVar, data = depression_network_and_dx_subgroup) #non sig
loss_in_nondep_network <- lm(total_fascicle_prop_lost_nondep_network~depGroupVar, data = depression_network_and_dx_subgroup) #non sig
```

>>>>

data_processed_as_of_20220209 <- read.csv(paste0(homedir, "/data/msdepression/data/erica_dac_pull/accession_numbers_tim_updtes_20220209.csv"), header = TRUE, stringsAsFactors = FALSE, sep = ",") #n=2738 new subjects added, 1124 were previously in Melissa's group, 2732 were already in our sample. Total n = 3862. Total accession # = 16,853

@@

```{r depression_unique_all_fascicles_together_last_scan}

#isolate out only the depressed group and healthy group, make a column that sums up the total prop lost)
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,]  %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice_tail(n = 1) %>% 
  mutate(total_fascicle_prop_lost = rowMeans(across(fascicle_names))) %>%
  ungroup()
##

@@

### Chi sq - compare # fdr corrected values in dep network to outside
table_for_chisq <-data.frame(rbind(c(5,35), c(30,17)), row.names = c("nondep_net", "dep_net"))
names(table_for_chisq) <- c("fdr05", "NS")
dep_network_age_effects_chi <- chisq.test(table_for_chisq) #p = 3.374 x 10^-6

@@

total_volume_lost_dep_vs_healthy_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1], dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == -1]) #mean dep = 28%, mean non_dep = 25%, p = 0.12

volume_lost_dep_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network) #mean dep_net = 35%, mean non_dep_net =  17%, p 2.2 x 10^-16

volume_lost_dep10_vs_nondep_network_unique <- t.test(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet_10_percent,
dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network) #mean dep net = 31%, mean non_dep_net = 17%, p 6.6 * 10^-15

#df for visreg
df_for_visreg <- as.data.frame(cbind(c(dep_and_healthy_groups_for_ICD_analysis$EMPI, dep_and_healthy_groups_for_ICD_analysis$EMPI), c(dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_indepnet, dep_and_healthy_groups_for_ICD_analysis$total_fascicle_prop_lost_nondep_network), c(rep(1,298), rep(2,298))))
names(df_for_visreg) <- c("EMPI", "prop_lost", "network")
df_for_visreg$network <- as.factor(df_for_visreg$network)

plot <- ggplot(df_for_visreg, aes(x=network, y = prop_lost, col=network)) +
  geom_violin() + 
  geom_jitter(shape=16, position=position_jitter(0.05)) + 
  geom_boxplot(width=0.1) + theme_minimal() + 
  stat_summary(fun.y=median, geom="point", size=2, color="red") + 
  scale_x_discrete(labels=c("1" = "Dep Network", "2" = "Non Dep Network"))

@@

#loss doesn't seem to be different between those with depression and those without
loss_in_dep_network <- lm(total_fascicle_prop_lost_indepnet~depGroupVar, data = depression_network_and_dx_subgroup) #non sig
loss_in_dep_network_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent~depGroupVar, data = depression_network_and_dx_subgroup) #non sig
loss_in_nondep_network <- lm(total_fascicle_prop_lost_nondep_network~depGroupVar, data = depression_network_and_dx_subgroup) #non sig, trend 0.09, mean dep = 19% loss, healthy 17% loss
```
